Precise predictions for same-sign W-boson scattering at the LHC

### 2018-03-04 Draft/distributionsNLO.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

In Figs.~(\ref{fig:distNLO1}-\ref{fig:distNLO3}), several differential distributions are shown.
All these predictions are performed at NLO accuracy at the order $\mathcal{O}(\alphas\alpha^6)$.

We start with Fig.~\ref{fig:distNLO1} which displays the invariant mass (left) and the rapidity separation (right) of the two tagging jets.
For high invariant mass, all predictions agree rather well.
On the other hand, for low invariant mass, the hierarchy present at the level of the cross section is here reproduced.
The VBS-approximated predictions ({\sc Bonsay} and {\sc Powheg-Box}) are lower than the full calculation ({\sc MoCaNLO}+{\sc Recola}).
The full calculation is rather well approximated by the hybrid VBS approximation implemented in {\sc MadGraph5\_aMC\-@NLO}.
Finally, {\sc VBFNLO} which includes as well $s$-channel contributions provides larger predictions at low invariant mass.
For the rapidity difference between the two tagging jets, the hierarchy between the predictions is rather similar.
Therefore, depending on the approximation used, it can vary by $\pm7\%$ and $\pm4\%$ with respect to the full computation at low invariant mass and low rapidity difference for the tagging jets, respectively

 \begin{figure*}[hbt!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/mjj_NLO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/dyj1j2_NLO.pdf}
\caption{\label{fig:distNLO1} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
}
\end{figure*}

@@

 \begin{figure*}[hbt!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/ptj1_NLO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/yj1_NLO.pdf}
\caption{\label{fig:distNLO2} Differential distributions in the transverse momentum (left) and rapidity of the hardest jet (right).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
}
\end{figure*}

@@

 \begin{figure*}[hbt!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/mll_NLO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/zmu_NLO.pdf}
\caption{\label{fig:distNLO3} Differential distributions in the invariant mass of the two charged leptons (left) and Zeppenfeld variable for the muon (right).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
}
\end{figure*}

In the end, the quality of the VBS-approximations is good up to $10\%$ in the fiducial region.
These differences are larger than at what is observed at LO.

@@

At the $s$-channel contributions are sizeable, their interferences with the $t$/$u$-channel can be of similar size in the phase-space region where the former are large.
This can be observed by comparing the predictions of {\sc VBFNLO} against the ones of {\sc MadGraph5\_aMC\-@NLO}.

Finally, the effect of EW corrections and non-factorisable contributions in the virtual corrections are usually small.
But they can be particularly large (about $10\%$) for large transverse momentum of the hardest jet.
These high-energy region of the phase space are where EW Sudakov logarithms become large.
Nonetheless these regions are rather suppressed and thus these effects are hardly visible at the level of the cross section.

>>>>

In Figs.~(\ref{fig:distNLO1}-\ref{fig:distNLO3}), several differential distributions are shown.
All these predictions are performed at NLO accuracy at the order $\mathcal{O}(\alphas\alpha^6)$.
In the upper panel, the absolute predictions are shown while in the lower panel, the ratio with respect to the full predictions are displayed.
The band corresponds to a seven-points variation of the factorisation and renormalisation scales.

We start with Fig.~\ref{fig:distNLO1} which displays the invariant mass (left) and the rapidity separation (right) of the two tagging jets.
For high invariant mass, all predictions agree rather well.
On the other hand, for low invariant mass, the hierarchy present at the level of the cross section is here reproduced.
The VBS-approximated predictions ({\sc Bonsay} and {\sc Powheg-Box}) are lower than the full calculation ({\sc MoCaNLO}+{\sc Recola}).
The full calculation is rather well approximated by the hybrid VBS approximation implemented in {\sc MadGraph5\_aMC\-@NLO}.
Finally, {\sc VBFNLO} which includes also $s$-channel contributions provides larger predictions at low invariant mass.
For the rapidity difference between the two tagging jets, the hierarchy between the predictions is rather similar.
Therefore, depending on the approximation used, it can vary by $\pm7\%$ and $\pm4\%$ with respect to the full computation at low invariant mass and low rapidity difference for the tagging jets, respectively

 \begin{figure*}[hbt!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/mjj_NLO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/dyj1j2_NLO.pdf}
\caption{\label{fig:distNLO1} Differential distributions in the invariant mass (left) and rapidity difference of the two tagging jets (right).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full predictions.
The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
}
\end{figure*}

@@

 \begin{figure*}[hbt!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/ptj1_NLO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/yj1_NLO.pdf}
\caption{\label{fig:distNLO2} Differential distributions in the transverse momentum (left) and rapidity of the hardest jet (right).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full predictions.
The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
}
\end{figure*}

@@

 \begin{figure*}[hbt!]
   \centering
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/mll_NLO.pdf}
   \includegraphics[width=0.4\textwidth,angle=0,clip=true,trim={0.4cm 2cm 0.cm 1.cm}]{figures/NLO/zmu_NLO.pdf}
\caption{\label{fig:distNLO3} Differential distributions in the invariant mass of the two charged leptons (left) and Zeppenfeld variable for the muon (right).
The LHC process considered is ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ at NLO accuracy and order $\mathcal{O}(\alpha_{\rm s}\alpha^6)$.
The description of the different programs used can be found in Sec.~\ref{subsec:codedescr}.
The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is the full predictions.
The band corresponds to a seven-points scale variation of the renormalisation and factorisation scale.
The predictions are obtained in the fiducial region described in Sec.~\ref{subsec:inputpar}.
}
\end{figure*}

In the end, the quality of the VBS-approximations is good up to $10\%$ in the fiducial region.
These differences are larger than at LO.

@@

As the $s$-channel contributions are sizeable, their interferences with the $t$/$u$-channel can be of similar size in the phase-space region where the former are large.
This can be observed by comparing the predictions of {\sc VBFNLO} against the ones of {\sc MadGraph5\_aMC\-@NLO}.

Finally, the effect of EW corrections and non-factorisable contributions in the virtual corrections are usually small.
But they can be relatively large (about $10\%$) for large transverse momentum of the hardest jet.
These high-energy region of the phase space are where EW Sudakov logarithms become large.
Nonetheless these regions are rather suppressed and thus these effects are hardly visible at the level of the cross section.

### 2018-03-04 Draft/input.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

The hadronic scattering processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massles flavour,\footnote{
For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO.} 
NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}
%Since this PDF set has no photonic density, photon-induced processes are not considered.
Initial-state collinear singularities are factorised according to the ${\overline{\rm MS}}$ scheme, consistently with what is done in NNPDF.

For the massive particles, the following masses and decay widths are used:
%
\begin{alignat}{2}
                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV.
\end{alignat}
%
The measured on-shell (OS) values for the masses and widths of the W and Z bosons are converted into pole values for the gauge bosons ($V=\PW,\PZ$) according to Ref.~\cite{Bardin:1988xt},
%
\begin{equation}
\begin{split}
        M_V &= \MVOS/\sqrt{1+(\GVOS/\MVOS)^2}\,, \\
   \Gamma_V &= \GVOS/\sqrt{1+(\GVOS/\MVOS)^2}.
\end{split}
\end{equation}
%
The EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj}, where
%
\begin{equation}
    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
\end{equation}
%
The numerical value of $\alpha$, corresponding to the choice of input parameters is
%
\begin{equation}
 \alpha = 7.555310522369 \times 10^{-3}.
\end{equation}
The CKM-Matrix is assumed to be diagonal, meaning that the mixing between different quark families is neglected.
The complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg,Denner:2006ic} is used throughout to treat unstable intermediate particles in a gauge-invariant manner.

The renormalisation and factorisation scales are set to the dynamical scale
%
\begin{equation}
\label{eq:defscale}
 \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}}, 
\end{equation}
%
defined via the transverse momenta of the two hardest identified jets.  
This choice of scale has been shown to provide stable NLO-QCD predictions \cite{Denner:2012dz}.

>>>>

The hadronic scattering processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massles flavour,\footnote{For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO.} 
NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in the program LHAPDF6~\cite{Buckley:2014ana} is 260000.}\footnote{Note that the {\sc Powheg-Box} uses its own implementation of the two loop running for $\alpha_{\rm s}$.}
%Since this PDF set has no photonic density, photon-induced processes are not considered.
Initial-state collinear singularities are factorised according to the ${\overline{\rm MS}}$ scheme, consistently with what is done in NNPDF.

For the massive particles, the following masses and decay widths are used:
%
\begin{alignat}{2}
                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV.
\end{alignat}
%
The measured on-shell (OS) values for the masses and widths of the W and Z bosons are converted into pole values for the gauge bosons ($V=\PW,\PZ$) according to Ref.~\cite{Bardin:1988xt},
%
\begin{equation}
\begin{split}
        M_V &= \MVOS/\sqrt{1+(\GVOS/\MVOS)^2}\,, \\
   \Gamma_V &= \GVOS/\sqrt{1+(\GVOS/\MVOS)^2}.
\end{split}
\end{equation}
%
The EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj}, where
%
\begin{equation}
    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
\end{equation}
%
The numerical value of $\alpha$, corresponding to the choice of input parameters is
%
\begin{equation}
 1/\alpha = 132.3572\ldots\,.
\end{equation}
The CKM-Matrix is assumed to be diagonal, meaning that the mixing between different quark families is neglected.
The complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg,Denner:2006ic} is used throughout to treat unstable intermediate particles in a gauge-invariant manner.

The renormalisation and factorisation scales are set to the dynamical scale
%
\begin{equation}
\label{eq:defscale}
 \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}}, 
\end{equation}
%
defined via the transverse momenta of the two hardest identified jets.\footnote{The renormalisation and factorisation scale employed in the {\sc Powheg-Box} slightly differ from the 
    one defined in Eq.~\eqref{eq:defscale}, as the momenta of two final-state quarks in the underlying-Born event are
    employed instead of those of the two hardest jets.\label{foot:powheg}} 
This choice of scale has been shown to provide stable NLO-QCD predictions \cite{Denner:2012dz}.

### 2018-03-04 Draft/introduction.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

Vector-boson scattering (VBS) at a hadron collider 
usually refers to the interaction of massive vector-bosons ($\PW^\pm,\PZ$),
radiated by partons (quarks) of the incoming protons, 
which in turn are deflected from the beam direction 
and enter the volume of the particle detectors.
As a consequence, the typical signature of VBS events
is characterised by two energetic jets 
and four fermions,
originating from the decay of the two vector bosons.
Among the possible diagrams,
the scattering process can be mediated by a Higgs boson
and involves in particular its longitudinal component.
The interaction of longitudinally polarised bosons is of particular interest, 
because the corresponding matrix elements feature unitarity cancellations 
that strongly depend on the actual structure of the Higgs sector.
A detailed study of this class of processes will therefore further constrain the Higgs couplings 
at a very different energy scale with respect to the Higgs boson mass,
and hint at, or exclude, non-Standard Model behaviours.

The VBS process involving two same-sign $\PW$ bosons has the largest signal-to-background ratio at the LHC of all the VBS processes:
evidence for it was found at the centre-of-mass energy of $8~\TeV$ already~\cite{Aad:2014zda,Khachatryan:2014sta},
and it has been recently observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} 
at $13\TeV$ as well.
Presently, the measurements of VBS processes are limited by statistics, but the situation will change in the near future.
On the theoretical side, 
it is thus of prime importance to provide predictions with systematic uncertainties
at least comparable to the current and envisaged experimental precision~\cite{CMS:2016rcn}.

$\PW^+\PW^+$ scattering is also the simplest VBS process to calculate, 
because the double-charge structure of the leptonic final state 
limits the number of partonic processes and total number of Feynman diagrams for each process.
Nonetheless, it possesses all features of VBS at the LHC and is thus representative of other VBS signatures.
Therefore, this process is the ideal candidate for a comparative study of the different simulation tools.

@@

\iffalse
The full gauge-invariant process including the $\PW^+\PW^+$ scattering 
 is $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$.
This final state receives three contributions at leading order (LO) whose coupling orders are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
They are commonly referred to as electroweak (EW), interference, and QCD contributions, respectively.%
\footnote{The EW contribution is sometimes referred to as the VBS contribution, even it involves also non-VBS contributions.}
\fi
After having defined the VBS process in Sec.~\ref{sec:definition} and having described the approximations of the various computer 
codes in Sec.~\ref{sec:details}, in Sec.~\ref{sec:LO} a leading-order (LO) study 
of the different contributions which lead to the production of two same-sign $\PW$ bosons and 
two jets is performed, as a function of typical VBS cuts. In the same section predictions for VBS from different tools are compared at 
the level of the cross section and differential distributions. The article continues in Sec.~\ref{sec:NLO} where the comparison is extended to the
NLO corrections to VBS. The effect of the inclusion of matching LO and NLO computations to parton-shower (PS) is 
discussed in Sec.~\ref{sec:matching}. Finally,
Sec.~\ref{sec:conclusion} contains a summary of the article and concluding remarks.

>>>>

Vector-boson scattering (VBS) at a hadron collider 
usually refers to the interaction of massive vector-bosons ($\PW^\pm,\PZ$),
radiated by partons (quarks) of the incoming protons, 
which in turn are deflected from the beam direction 
and enter the volume of the particle detectors.
As a consequence, the typical signature of VBS events
is characterised by two energetic jets 
and four fermions,
originating from the decay of the two vector bosons.
Among the possible diagrams,
the scattering process can be mediated by a Higgs boson
and involves in particular its longitudinal component.
The interaction of longitudinally polarised bosons is of particular interest, 
because the corresponding matrix elements feature unitarity cancellations 
that strongly depend on the actual structure of the Higgs sector of the Standard Model (SM).
A detailed study of this class of processes will therefore further constrain the Higgs couplings 
at a very different energy scale with respect to the Higgs boson mass,
and hint at, or exclude, non-Standard Model behaviours.

The VBS process involving two same-sign $\PW$ bosons has the largest signal-to-background ratio of all the VBS processes at the Large Hadron Collider (LHC):
evidence for it was found at the centre-of-mass energy of $8~\TeV$ already~\cite{Aad:2014zda,Khachatryan:2014sta},
and it has been recently observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} 
at $13\TeV$ as well.
Presently, the measurements of VBS processes are limited by statistics, but the situation will change in the near future.
On the theoretical side, 
it is thus of prime importance to provide predictions with systematic uncertainties
at least comparable to the current and envisaged experimental precision~\cite{CMS:2016rcn}.

$\PW^+\PW^+$ scattering is also the simplest VBS process to calculate, 
because the double-charge structure of the leptonic final state 
limits the number of partonic processes and total number of Feynman diagrams for each process.
Nonetheless, it possesses all features of VBS at the LHC and is thus representative of other VBS signatures.
Therefore, it is the ideal candidate for a comparative study of the different simulation tools.

@@

\iffalse
The full gauge-invariant process including the $\PW^+\PW^+$ scattering 
 is $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$.
This final state receives three contributions at leading order (LO) whose coupling orders are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
They are commonly referred to as electroweak (EW), interference, and QCD contributions, respectively.%
\footnote{The EW contribution is sometimes referred to as the VBS contribution, even it involves also non-VBS contributions.}
\fi
This article starts with the definition of the VBS process in Sec.~\ref{sec:definition}.
After having described the approximations of the various computer 
codes in Sec.~\ref{sec:details}, in Sec.~\ref{sec:LO} a leading-order (LO) study 
of the different contributions which lead to the production of two same-sign $\PW$ bosons and 
two jets is performed, as a function of typical VBS cuts. In the same section predictions for VBS from different tools are compared at 
the level of the cross section and differential distributions. The article continues in Sec.~\ref{sec:NLO} where the comparison is extended to the
NLO corrections to VBS. The effect of the inclusion of matching LO and NLO computations to parton-shower (PS) is 
discussed in Sec.~\ref{sec:matching}. Finally,
Sec.~\ref{sec:conclusion} contains a summary of the article and concluding remarks.

### 2018-03-04 Draft/process.tex
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

We now turn to discuss the various approximations which are implemented in computer programs for the EW contribution at
$\mathcal{O}{\left(\alpha^{6}\right)}$. Since we are mostly interested in 
the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex, may appear justified to approximate the 
full process by considering just those diagrams which contain the $2\rightarrow 2$ scattering process as a sub-part.
However, this set of contributions is not gauge invariant.
In order ensure gauge invariance, an on-shell projection of the incoming and outgoing $\PW$ bosons should be performed {\bf MZ CITE}.
Unfortunately, the former momenta are space-like and thus a simple on-shell projection is not possible.
Instead, one can keep the $\PW$ boson legs connected to the external quark line off-shell while the ones connected 
to the final-state leptons, which are already time-like, are put on-shell. \ZM{is this still gauge invariant? if so, one should change 
the sentence above ``In order to ensure..''}
Then the polarisation of the gauge boson is accommodated following for example the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
Such an approximation is usually called effective vector-boson approximation (EVBA) \cite{Dawson:1984gx,Duncan:1985vj,Cahn:1983ip}.

>>>>

We now discuss the various approximations which are implemented in computer programs for the EW contribution at order $\mathcal{O}{\left(\alpha^{6}\right)}$.
Since we are mostly interested in 
the scattering of two $\PW$ gauge bosons, which includes the quartic gauge-boson vertex, may appear justified to approximate the 
full process by considering just those diagrams which contain the $2\rightarrow 2$ scattering process as a sub-part.
However, this set of contributions is not gauge invariant.
In order ensure gauge invariance, an on-shell projection of the incoming and outgoing $\PW$ bosons should be performed {\bf MZ CITE}.
Unfortunately, the former momenta are space-like and thus a simple on-shell projection is not possible.
Instead, one can keep the $\PW$ boson legs connected to the external quark line off-shell while the ones connected 
to the final-state leptons, which are already time-like, are put on-shell. \ZM{is this still gauge invariant? if so, one should change 
the sentence above ``In order to ensure..''}
Then the polarisation of the gauge boson is accommodated following for example the implementations of Refs.~\cite{Kuss:1995yv,Accomando:2006hq}.
Such an approximation is usually called effective vector-boson approximation (EVBA) \cite{Dawson:1984gx,Duncan:1985vj,Cahn:1983ip}.

### 2018-03-04 Draft/scanLO.tex
Few comments discussed with Marco addressed
Significant modifications of Mathieu: corrections/improvements, all labels should now be consistent

In Fig.~\ref{fig:ratio2d_LO}, ratios of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ is shown.\footnote{In Fig.~\ref{fig:ratio2d_LO}, the level of the accuracy of the predictions in each bin is around a per mille.}
Two plots are displayed: the ratios of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation.
In the first case, the approximation is good within $\pm10\%$ over the whole range apart in the low invariant-mass region at both low and large rapidity difference.
The low rapidity-difference region possesses remnants of the tri-bosons contributions that have a di-jet invariant mass around the $\PW$-boson mass.
It is therefore expected that the $|t|^2 + |u|^2$ approximation fails in this region.
The second plot, where the $|s|^2 + |t|^2 + |u|^2$ approximation is considered, displays a better behaviour in the previously mentioned region.
The full calculation is approximated at the level of $\pm5\%$ apart in the region where $\Delta y_{\Pj\Pj} < 2$.

\begin{figure*}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/ratio_tu.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
\caption{Ratio of cross sections per bin in the plan $\left(m_{\Pj\Pj}, |\Delta y_{\Pj\Pj}| \right)$ at LO \emph{i.e.}\ order $\mathcal{O}(\alpha^6)$.
Ratio of approximated squared amplitudes over the full matrix element.
The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).
The cuts applied are the one of of Sec.~\ref{subsec:inputpar} and no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.} 
\label{fig:ratio2d_LO}
\end{figure*}
% As explained previously, the low di-jet invariant mass and low jet rapidity separation regions are dominated by tri-boson production.

\ZM {the following is rather confusing, I will drop it from here and discuss it in the NLO-fiducial section}
Therefore, the \emph{inclusive} study at NLO is only performed in the region 
%
\begin{equation}
\label{eq:inclusive}
	m_{jj} > 200\GeV\, \qquad {\rm and} \qquad |\Delta y_{jj}| > 2 .
\end{equation}
%
Hence, the differences arising at NLO in this fiducial region originate solely from NLO effects.

>>>>

In Fig.~\ref{fig:ratio2d_LO}, ratios of double-differential cross sections in the plane $\left(m_{\Pj\Pj}, \Delta y_{\Pj\Pj}\right)$ are shown.\footnote{In Fig.~\ref{fig:ratio2d_LO}, the level of the accuracy of the predictions in each bin is around a per mille.}
Two plots are displayed: the ratios of the $|t|^2 + |u|^2$ and $|s|^2 + |t|^2 + |u|^2$ approximations over the full calculation.
In the first case, the approximation is good within $\pm10\%$ over the whole range apart in the low invariant-mass region at both low and large rapidity difference.
The low rapidity-difference region possesses remnants of the tri-bosons contributions that have a di-jet invariant mass around the $\PW$-boson mass.
It is therefore expected that the $|t|^2 + |u|^2$ approximation fails in this region.
The second plot, where the $|s|^2 + |t|^2 + |u|^2$ approximation is considered, displays a better behaviour in the previously mentioned region.
The full calculation is approximated at the level of $\pm5\%$ apart in the region where $\Delta y_{\Pj\Pj} < 2$.

\begin{figure*}[hbt]
\centering
\includegraphics[scale=0.395]{figures/scanfigures/ratio_tu.pdf}
\includegraphics[scale=0.395]{figures/scanfigures/ratio_stu.pdf}
\caption{Ratios of double-differential distributions in the variables the variables $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ at LO \emph{i.e.}\ order $\mathcal{O}(\alpha^6)$.
Ratio of approximated squared amplitudes over the full matrix element.
The approximated squared amplitudes are computed as $|\mathcal{A}|^2 \sim |t|^2 + |u|^2$ (left) and $|\mathcal{A}|^2 \sim |s|^2 + |t|^2 + |u|^2$ (right).
The cuts applied are the one of of Sec.~\ref{subsec:inputpar} and no cuts on $m_{\Pj\Pj}$ and $|\Delta y_{\Pj\Pj}|$ are applied.} 
\label{fig:ratio2d_LO}
\end{figure*}
% As explained previously, the low di-jet invariant mass and low jet rapidity separation regions are dominated by tri-boson production.

% Therefore, the \emph{inclusive} study at NLO is only performed in the region 
% %
% \begin{equation}
% \label{eq:inclusive}
% 	m_{jj} > 200\GeV\, \qquad {\rm and} \qquad |\Delta y_{jj}| > 2 .
% \end{equation}
% %
% Hence, the differences arising at NLO in this fiducial region originate solely from NLO effects.
